Capstone Movielens Report

### 2025-05-18 reports/capstone-movielens.site/01.intro.Rmd

Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
```{r eval=FALSE }
if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

>>>>

Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
```{r}
if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

### 2025-05-18 reports/capstone-movielens.site/04.appendix.Rmd

::: { #func.mean_reg.params.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;

@@

Plots a graph based on the dataset passed in the [data](#func.mean_reg.params.data) parameter, using both points and a line.

@@

::: { #func.mean_reg.params.data .sidebar }
  - **data:** Dataset to use for the plot;

:::
::: { #func.mean_reg.params.title .sidebar }
  - **title:** Title of the plot;

:::
::: { #func.mean_reg.params.xname .sidebar }
  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;

:::
::: { #func.mean_reg.params.yname .sidebar }
  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;

:::
::: { #func.mean_reg.params.xlabel .sidebar }
  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;

:::
::: { #func.mean_reg.params.ylabel .sidebar }
  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;

:::
::: { #func.mean_reg.params. .sidebar }
  - **line_col = blue:** The line color;

:::
::: { #func.mean_reg.params. .sidebar }
  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.

>>>>

::: { #func.union_cv_results.params.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;

@@

Plots a graph based on the dataset passed in the [data](#func.data.plot.params.data) parameter, using both points and a line.

@@

::: { #func.data.plot.params.data .sidebar }
  - **data:** Dataset to use for the plot;

:::
::: { #func.data.plot.params.title .sidebar }
  - **title:** Title of the plot;

:::
::: { #func.data.plot.params.xname .sidebar }
  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;

:::
::: { #func.data.plot.params.yname .sidebar }
  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;

:::
::: { #func.data.plot.params.xlabel .sidebar }
  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;

:::
::: { #func.data.plot.params.ylabel .sidebar }
  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;

:::
::: { #func.data.plot.params.line_col .sidebar }
  - **line_col = blue:** The line color;

:::
::: { #func.data.plot.params.normalize .sidebar }
  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
